---
title: "Story Group Analysis"
format: html
editor: visual
---


## Section 1: Load Data

```{r}
# Load necessary libraries
library(readxl)
library(ggplot2)
library(dplyr)

# Step 1: Load the Excel file into R
story_df <- read_xlsx(file.choose())

```

## Section 2: Drop Qualtrics Metadata Columns

```{r}
library(dplyr)

story_df <- story_df %>%
  select(-c(
    StartDate, EndDate, Status, IPAddress, Progress, Finished, RecordedDate, ResponseId,
    RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude,
    DistributionChannel, UserLanguage, `Duration (in seconds)`
  ))

# Display the updated dataframe
story_df <- story_df %>%
  select(
-contains("15-second pause"),
    -contains("20-second delay"),
    - contains("pause_"),
    - contains("Q3_"))



```

## Section 3: Headphone Check Filtering

failed headphone checks 6.0 (correct answer) for column Q2...22 5.0 (correct answer) for column Q2...23 6.0 (correct answer) for column Q2...24

Anyone who got a wrong answer will be removed! Then, I will count the number of IDs (people still left)

```{r}
# Check individual conditions
story_clean <- story_df[-1, ]

# Convert columns to numeric
story_clean <- story_clean %>%
  mutate(across(c(`Q1...22`, `Q2...23`, `Q3...24`), as.numeric))

story_df <- story_df %>%
  mutate(across(c(`Q1...22`, `Q2...23`, `Q3...24`), as.numeric))

# Handle missing values
story_clean <- story_clean %>%
  filter(!is.na(`Q1...22`) & !is.na(`Q2...23`) & !is.na(`Q3...24`)) %>%
  filter(`Q1...22` == 6.0 & 
         `Q2...23` == 5.0 & 
         `Q3...24` == 6.0)

story_df <- story_df %>%
  filter(!is.na(`Q1...22`) & !is.na(`Q2...23`) & !is.na(`Q3...24`)) %>%
  filter(`Q1...22` == 6.0 & 
         `Q2...23` == 5.0 & 
         `Q3...24` == 6.0)

```

## Section 4: Build NES_combined_df (Canonical Version)

Constructs NES_combined_df with SRQ, Familiar, Enjoy, and NES1-4 for all 8 audio stimuli using the make_audio_nes_df() helper. All models below draw from this dataframe.

```{r}
# MEGA DATAFRAME REMAKING (ALL-IN-ONE)
# Adds SRQ + Familiar + Enjoy columns per audio
# Keeps SRQ==2 rows (does NOT drop them just because ratings are NA)
# Computes Average ONLY from the 4 NES items (never from SRQ/Familiar/Enjoy)
# Then renames NES items, adds AudNum, rbinds, and adds grouping columns

library(dplyr)
library(tidyr)
library(ggplot2)

# Helper: build one audio NES df safely
make_audio_nes_df <- function(df, audnum, srq_col, fam_col, enjoy_col, nes_cols) {
  out <- df %>%
    select(ID, all_of(srq_col), all_of(fam_col), all_of(enjoy_col), all_of(nes_cols)) %>%
    rename(
      SRQ      = all_of(srq_col),
      Familiar = all_of(fam_col),
      Enjoy    = all_of(enjoy_col)
    ) %>%
    mutate(
      across(c(SRQ, Familiar, Enjoy, all_of(nes_cols)), ~ as.numeric(as.character(.)))
    ) %>%
    mutate(
      Average = if_else(
        rowSums(!is.na(across(all_of(nes_cols)))) > 0,
        rowMeans(across(all_of(nes_cols)), na.rm = TRUE),
        NA_real_
      ),
      AudNum = audnum
    ) %>%
    filter(!is.na(ID), !is.na(SRQ)) %>%   # keep SRQ==2 rows even if ratings are NA
    rename(
      NES1 = all_of(nes_cols[1]),
      NES2 = all_of(nes_cols[2]),
      NES3 = all_of(nes_cols[3]),
      NES4 = all_of(nes_cols[4])
    )

  out
}

# Build each audio dataframe 
Aud_01_NES_df <- make_audio_nes_df(
  df = story_df, audnum = 1,
  srq_col   = "Audio1...29",
  fam_col   = "Audio1_1...35",
  enjoy_col = "Audio1_1...36",
  nes_cols  = c("Audio1_1...37","Audio1_1...38","Audio1_1...39","Audio1_1...40")
)

Aud_02_NES_df <- make_audio_nes_df(
  df = story_df, audnum = 2,
  srq_col   = "Audio2...52",
  fam_col   = "Audio2_1...58",
  enjoy_col = "Audio2_1...59",
  nes_cols  = c("Audio2_1...60","Audio2_1...61","Audio2_1...62","Audio2_1...63")
)

Aud_05_NES_df <- make_audio_nes_df(
  df = story_df, audnum = 5,
  srq_col   = "Audio5...77",
  fam_col   = "Audio5_1...83",
  enjoy_col = "Audio5_1...84",
  nes_cols  = c("Audio5_1...85","Audio5_1...86","Audio5_1...87","Audio5_1...88")
)

Aud_06_NES_df <- make_audio_nes_df(
  df = story_df, audnum = 6,
  srq_col   = "Audio6...100",
  fam_col   = "Audio6_1...106",
  enjoy_col = "Audio6_1...107",
  nes_cols  = c("Audio6_1...108","Audio6_1...109","Audio6_1...110","Audio6_1...111")
)

Aud_09_NES_df <- make_audio_nes_df(
  df = story_df, audnum = 9,
  srq_col   = "Audio9...123",
  fam_col   = "Audio9_1...129",
  enjoy_col = "Audio9_1...130",
  nes_cols  = c("Audio9_1...131","Audio9_1...132","Audio9_1...133","Audio9_1...134")
)

Aud_10_NES_df <- make_audio_nes_df(
  df = story_df, audnum = 10,
  srq_col   = "Audio10...146",
  fam_col   = "Audio10_1...152",
  enjoy_col = "Audio10_1...153",
  nes_cols  = c("Audio10_1...154","Audio10_1...155","Audio10_1...156","Audio10_1...157")
)

Aud_11_NES_df <- make_audio_nes_df(
  df = story_df, audnum = 11,
  srq_col   = "Audio11...169",
  fam_col   = "Audio11_1...175",
  enjoy_col = "Audio11_1...176",
  nes_cols  = c("Audio11_1...177","Audio11_1...178","Audio11_1...179","Audio11_1...180")
)

Aud_12_NES_df <- make_audio_nes_df(
  df = story_df, audnum = 12,
  srq_col   = "Audio12...192",
  fam_col   = "Audio12_1...198",
  enjoy_col = "Audio12_1...199",
  nes_cols  = c("Audio12_1...200","Audio12_1...201","Audio12_1...202","Audio12_1...203")
)

# Combine all audio dataframes 
NES_combined_df <- bind_rows(
  Aud_01_NES_df,
  Aud_02_NES_df,
  Aud_05_NES_df,
  Aud_06_NES_df,
  Aud_09_NES_df,
  Aud_10_NES_df,
  Aud_11_NES_df,
  Aud_12_NES_df
)

# Quick checks (optional)
str(NES_combined_df)
summary(NES_combined_df)
head(NES_combined_df)

# Downstream grouping columns 
NES_combined_df <- NES_combined_df %>%
  mutate(
    Duration = ifelse(AudNum %in% c(1, 2, 5, 6), "500 ms", "3000 ms"),
    Timbre   = ifelse(AudNum %in% c(1, 2, 9, 10, 11, 12), "sine",
                      ifelse(AudNum %in% c(5, 6), "noise", "Other")),
    warble   = ifelse(AudNum %in% c(1, 2, 5, 6, 9, 10), "none",
                      ifelse(AudNum %in% c(11, 12), "6 Hz", "Other")),
    AttackTimes = ifelse(AudNum %in% c(1, 5, 9, 11), "fast", "slow")
  )

# View final
head(NES_combined_df)
```

Add audio stimulus labels (needed for figures and descriptives)

```{r}
library(dplyr)

NES_combined_df <- NES_combined_df %>%
  mutate(Audio = case_when(
    AudNum == 1 ~ "5SNF1",
    AudNum == 2 ~ "5SNS2",
    AudNum == 5 ~ "5NNF5",
    AudNum == 6 ~ "5NNS6",
    AudNum == 9 ~ "3SNF9",
    AudNum == 10 ~ "3SNS10",
    AudNum == 11 ~ "3S6F11",
    AudNum == 12 ~ "3S6S12"  ))

```

## Section 5: Factor Setup, Reference Levels, and SRQ Binary

```{r}
library(dplyr)
library(lme4)
library(lmerTest)
library(car)
library(MuMIn)
library(broom.mixed)

NES_combined_df <- NES_combined_df %>%
  mutate(
    Duration = factor(Duration),
    Timbre = factor(Timbre),
    warble = factor(warble),
    AttackTimes = factor(AttackTimes),
    ID = factor(ID),
    SRQ = as.numeric(SRQ),
    SRQ_yes = ifelse(SRQ == 1, 1, ifelse(SRQ == 2, 0, NA)) # binary outcome
  )

# Reference levels (match your current choices)
NES_combined_df <- NES_combined_df %>%
  mutate(
    Timbre = relevel(Timbre, ref = "sine"),
    Duration = relevel(Duration, ref = "3000 ms"),
    warble = relevel(warble, ref = "none"),
    AttackTimes = relevel(AttackTimes, ref = "slow")
  )

```

## Section 6: Descriptive Statistics

### 6a: Familiarity and Enjoyment (Story Group)

```{r}
NES_combined_df %>%
  summarise(
    Familiar_mean = mean(Familiar, na.rm = TRUE),
    Familiar_sd   = sd(Familiar, na.rm = TRUE),
    Enjoy_mean    = mean(Enjoy, na.rm = TRUE),
    Enjoy_sd      = sd(Enjoy, na.rm = TRUE),
    n             = n()
  )

```

### 6b: Story Yes/No Rate by Audio

```{r}
# Overall yes rate
mean(NES_combined_df$SRQ_yes, na.rm = TRUE)

# By audio
story_by_audio <- NES_combined_df %>%
  group_by(AudNum) %>%
  summarise(
    yes_prop = mean(SRQ_yes, na.rm = TRUE),
    yes_n = sum(SRQ_yes == 1, na.rm = TRUE),
    n = sum(!is.na(SRQ_yes))
  )
story_by_audio

```

### 6c: Overall NES Scores

```{r}
# Overall M and SD (across all trials)
NES_overall <- NES_combined_df %>%
  summarise(
    M = mean(Average, na.rm = TRUE),
    SD = sd(Average, na.rm = TRUE)
  )
print(NES_overall)

# Range of stimulus means (min to max across the 8 stimuli)
NES_by_stimulus <- NES_combined_df %>%
  group_by(Audio) %>%
  summarise(M = mean(Average, na.rm = TRUE), .groups = "drop")

cat("NES range:", round(min(NES_by_stimulus$M), 2), "to", round(max(NES_by_stimulus$M), 2))
print(NES_by_stimulus)
```

## Section 7: Figure 1 — Story Yes/No Stacked Percent Barplot

```{r}
# Step 1: Create HadMem_df with IDs and audio responses
HadMem_df <- story_clean %>% 
  select(
    Audio1 = Audio1...29,
    Audio2 = Audio2...52,
    Audio5 = Audio5...77,
    Audio6 = Audio6...100,
    Audio9 = Audio9...123,
    Audio10 = Audio10...146,
    Audio11 = Audio11...169,
    Audio12 = Audio12...192
  )

# Check the structure of the new dataframe
str(HadMem_df)

# View the first few rows
head(HadMem_df)
```

```{r}

# Convert columns to numeric to ensure proper counting
HadMem_df[] <- lapply(HadMem_df, as.numeric)

# Count 1.0 and 2.0 in each column
count_results <- lapply(HadMem_df, function(x) {
  c(
    "1.0" = sum(x == 1.0, na.rm = TRUE),
    "2.0" = sum(x == 2.0, na.rm = TRUE)
  )
})

# Convert the results to a data frame for better display
count_df <- as.data.frame(count_results)

# View the counts
print(count_df)

# Assuming count_df has rows for 1.0 (Yes) and 2.0 (No) responses
# and columns for each audio clip

```

```{r}
names(count_df) <- c("5SNF1", "5SNS2", "5NNF5", "5NNS6", "3SNF9", "3SNS10", "3S6F11", "3S6S12")

print(count_df)
```

```{r}
# --- Clean + stacked % plot (APA export) ---

# 1) Force numeric (fixes "invalid 'type' (character)" errors)
count_df_num <- as.data.frame(lapply(count_df, function(x) as.numeric(as.character(x))))
rownames(count_df_num) <- rownames(count_df)

# 2) Drop accidental column named "Audio" if it exists
if ("Audio" %in% colnames(count_df_num)) {
  count_df_num <- count_df_num[, colnames(count_df_num) != "Audio", drop = FALSE]
}

# 3) Make matrix (rows are responses, cols are stimuli)
mat <- as.matrix(count_df_num)

# Your coding: row 1 = 1.0 (Yes), row 2 = 2.0 (No)
rownames(mat) <- c("Yes", "No")
mat <- mat[c("Yes", "No"), , drop = FALSE]   # ensures Yes is bottom in stacked bars

# 4) Percent within each stimulus (each column sums to 100)
pct <- prop.table(mat, margin = 2) * 100

# Overall mean %Yes (count-weighted)
overall_yes <- sum(mat["Yes", ], na.rm = TRUE) / sum(mat, na.rm = TRUE) * 100

# Clean x labels (remove R's "X" prefix for names starting with digits)
labs <- colnames(pct)
labs <- gsub("^X", "", labs)

# Colors (match your current palette)
barplot_colors <- c("Yes" = "skyblue", "No" = "salmon")

# --- APA export ---
png("figure1_story_frequency_percent_stacked.png",
    width = 6.5, height = 4.5, units = "in", res = 300, family = "Arial")

# Give space on right for legend; big bottom margin for rotated labels
par(mar = c(8, 4, 1, 6) + 0.1)

bp <- barplot(pct,
              beside = FALSE,
              col = barplot_colors,
              ylim = c(0, 100),
              ylab = "Percent of Trials",
              xlab = "",
              names.arg = labs,
              las = 2,
              cex.lab = 1.1,
              cex.axis = 0.95)

# Mean line (~66%)
abline(h = overall_yes, lty = 2, lwd = 2)

# Legend outside the plot area (right side)
par(xpd = NA)
legend(x = par("usr")[2] + 0.2, y = 100,
       legend = c("Yes", "No"),
       fill = barplot_colors,
       bty = "n",
       cex = 1.0)
par(xpd = FALSE)

# Label only the YES segment (bottom) to reduce clutter
yes_vals <- pct["Yes", ]
text(x = bp,
     y = yes_vals / 2,
     labels = sprintf("%.0f%%", yes_vals),
     cex = 0.8,
     col = "white",
     font = 2)

dev.off()

```

## Section 8: Logistic GLMM — Story Yes/No 

Logistic GLMM: SRQ_yes ~ Duration + Timbre + warble + AttackTimes + (1|ID)

```{r}
story_glmm <- glmer(
  SRQ_yes ~ Duration + Timbre + warble + AttackTimes + (1 | ID),
  data = NES_combined_df,
  family = binomial(link = "logit")
)

summary(story_glmm)
car::Anova(story_glmm, type = 3)
tidy(story_glmm, effects = "fixed", conf.int = TRUE, exponentiate = TRUE)  # odds ratios

```

```{r}
# GLMM R² and formatted output #
cat("GLMM R² VALUES\n")
r2_glmm <- MuMIn::r.squaredGLMM(story_glmm)
cat(sprintf("Marginal R² (fixed effects only): %.4f\n", r2_glmm[1]))
cat(sprintf("Conditional R² (fixed + random):  %.4f\n", r2_glmm[2]))
```

## Section 9: NES Linear Mixed-Effects Model  

LMM: Average ~ Duration + Timbre + warble + AttackTimes + (1|ID)

```{r}
nes_df <- NES_combined_df %>% filter(!is.na(Average))

nes_lmm <- lmer(
  Average ~ Duration + Timbre + warble + AttackTimes + (1 | ID),
  data = nes_df,
  REML = TRUE
)

summary(nes_lmm)
car::Anova(nes_lmm, type = 3)
tidy(nes_lmm, effects = "fixed", conf.int = TRUE)
MuMIn::r.squaredGLMM(nes_lmm)

```

## Section 10: Load Context Data and Between-Group Analysis

Requires context_aud_long.csv from the context .qmd (run that first).

```{r}
library(readr)

aud_long <- read_csv(file.choose())

```

### 10a: Construct Audio-Level Summary Dataframes

```{r}
library(dplyr)

story_audio_summary <- NES_combined_df %>%
  mutate(
    SRQ = as.numeric(SRQ),
    SRQ_yes = if_else(SRQ == 1, 1, 0)
  ) %>%
  group_by(AudNum, Duration, Timbre, warble, AttackTimes) %>%
  summarise(
    story_yes_prop = mean(SRQ_yes, na.rm = TRUE),
    NES_mean       = mean(Average, na.rm = TRUE),
    Familiar_mean  = mean(Familiar, na.rm = TRUE),
    Enjoy_mean     = mean(Enjoy, na.rm = TRUE),
    n_story        = n(),
    .groups = "drop"
  )

story_audio_summary

```

```{r}
library(dplyr)
library(stringr)

library(dplyr)

# Summarise context-ease per audio
context_audio_summary <- aud_long %>%
  group_by(Audio) %>%
  summarise(
    ContextEase_mean = mean(Rating, na.rm = TRUE),
    ContextEase_sd   = sd(Rating, na.rm = TRUE),
    n_context        = n(),
    .groups = "drop"
  )

context_audio_summary

```

```{r}
library(dplyr)

audio_feature_key <- tibble::tribble(
  ~Audio,     ~Duration,   ~Timbre,  ~warble, ~AttackTimes,
  "5SNF1",    "500 ms",    "sine",   "none",  "fast",
  "5SNS2",    "500 ms",    "sine",   "none",  "slow",
  "5NNF5",    "500 ms",    "noise",  "none",  "fast",
  "5NNS6",    "500 ms",    "noise",  "none",  "slow",
  "3SNF9",    "3000 ms",   "sine",   "none",  "fast",
  "3SNS10",   "3000 ms",   "sine",   "none",  "slow",
  "3S6F11",   "3000 ms",   "sine",   "6 Hz",  "fast",
  "3S6S12",   "3000 ms",   "sine",   "6 Hz",  "slow"
) %>%
  mutate(
    Duration = factor(Duration),
    Timbre = factor(Timbre),
    warble = factor(warble),
    AttackTimes = factor(AttackTimes)
  )

context_audio_summary <- context_audio_summary %>%
  left_join(audio_feature_key, by = "Audio")

context_audio_summary

```

```{r}

context_audio_summary <- context_audio_summary %>%
    mutate(AudNum = as.numeric(str_extract(Audio, "\\d+$")))

# Verify the mapping looks right
context_audio_summary %>% select(Audio, AudNum)

audio_level_df <- story_audio_summary %>%
    left_join(context_audio_summary, by = "AudNum")

```

### 10b: Between-Group Regression 

Tests whether mean ease-of-context ratings predict the proportion of "yes" story responses (stimulus-level, n = 8).

```{r}
# Pearson correlation test
test <- cor.test(audio_level_df$ContextEase_mean, audio_level_df$story_yes_prop)
test
```

```{r}
model <- lm(story_yes_prop ~ ContextEase_mean, data = audio_level_df)
model
summary(model)
```
```{r}
# Regression CIs and full statistics 
cat("95% CI for regression coefficients:\n")
print(confint(model))
cat("\n")

coef_summary <- summary(model)$coefficients
r_sq <- summary(model)$r.squared
adj_r_sq <- summary(model)$adj.r.squared
f_stat <- summary(model)$fstatistic
ci <- confint(model)

cat("Between-group regression\n")
cat(sprintf("B = %.2f, SE = %.2f, t(%.0f) = %.2f, p = %.3f, 95%% CI [%.2f, %.2f]\n",
    coef_summary[2,1], coef_summary[2,2], f_stat[3], coef_summary[2,3], 
    coef_summary[2,4], ci[2,1], ci[2,2]))
cat(sprintf("R² = %.2f, adjusted R² = %.2f\n", r_sq, adj_r_sq))
cat(sprintf("F(%.0f, %.0f) = %.2f, p = %.3f\n", f_stat[2], f_stat[3], f_stat[1],
    pf(f_stat[1], f_stat[2], f_stat[3], lower.tail = FALSE)))
```

### 10c: Figure 3 — Context Ease vs. Story Yes Proportion

```{r}
library(ggplot2)

# Fit the model
model_story_from_context <- lm(story_yes_prop ~ ContextEase_mean, data = audio_level_df)
summary(model_story_from_context)

# Make AudNum a factor for discrete colors/legend
audio_level_df <- audio_level_df %>%
  mutate(AudNum = factor(AudNum))

# Plot WITH color + legend using AudNum
figure_story_from_context <- ggplot(
  audio_level_df,
  aes(x = ContextEase_mean, y = story_yes_prop, color = AudNum)
) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(
    method = "lm",
    se = TRUE,
    color = "black",
    linetype = "solid",
    linewidth = 1,
    aes(group = 1)  # one regression line across all points
  ) +
  labs(
    x = "Mean Context Ease",
    y = "Story Yes Proportion",
    color = "Audio\nStimulus (AudNum)"
  ) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(
    text = element_text(family = "Arial", size = 10),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 9),
    legend.position = "right",
    plot.title = element_blank()
  )

# Save
ggsave(
  filename = "figure_storyYesProp_vs_contextEase_AudNum.png",
  plot = figure_story_from_context,
  width = 6.5,
  height = 4.5,
  dpi = 300,
  units = "in"
)


```

## Section 11: Figure 2 — Combined NES + Ease-of-Context Violin 

Uses aud_long (Section 10) and NES_combined_df (Section 4).

```{r}
library(ggplot2)
library(patchwork)
library(RColorBrewer)

# Shared palette (locks identical colors to the same Audio level across BOTH plots)
audio_levels <- sort(unique(c(as.character(NES_combined_df$Audio),
                              as.character(aud_long$Audio))))

shared_pal <- setNames(
  brewer.pal(max(3, min(8, length(audio_levels))), "Set2")[1:length(audio_levels)],
  audio_levels
)

# Figure 2 (NES)
figure2 <- ggplot(NES_combined_df, aes(x = factor(Audio), y = Average, fill = factor(Audio))) +
  geom_violin(alpha = 0.7, trim = FALSE) +
  geom_jitter(width = 0.15, alpha = 0.4, size = 1.5, color = "gray20") +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 4, color = "red") +
  scale_fill_manual(values = shared_pal) +
  scale_x_discrete(labels = NULL) +                 # remove individual x tick labels
  labs(
    x = "Stimulus",
    y = "NES ratings",
    fill = "Stimulus"                               # legend title
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 10),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 9),
    axis.text.x = element_blank(),                  # hide x-axis tick text
    axis.ticks.x = element_blank(),                 # hide x-axis tick marks
    legend.position = "right",
    legend.text = element_text(size = 9),
    legend.title = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    plot.title = element_blank(),
    plot.subtitle = element_blank()
  )

# Figure 4 (Ease of context) 
figure4 <- ggplot(aud_long, aes(x = factor(Audio), y = Rating, fill = factor(Audio))) +
  geom_violin(alpha = 0.7, trim = FALSE) +
  geom_jitter(width = 0.15, alpha = 0.4, size = 1.5, color = "gray20") +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 4, color = "red") +
  scale_y_continuous(limits = c(1, 6), breaks = NULL) +  # remove 1–6 tick labels
  scale_fill_manual(values = shared_pal) +
  scale_x_discrete(labels = NULL) +                      # remove individual x tick labels
  labs(
    x = "Stimulus",
    y = "Ease of Context Ratings",
    fill = "Stimulus"
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 10),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 9),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 9),
    legend.title = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    plot.title = element_blank()
  )

# Stack + shared legend 
stacked_fig <- figure2 / figure4 + plot_layout(guides = "collect")

ggsave(
  "figure2_figure4_stacked.png",
  plot = stacked_fig,
  width = 6.5,
  height = 9,
  dpi = 300,
  units = "in"
)


```

